Hydras \& Co.

### 2023-08-10 doc/chap-intro-goedel.tex
corrections chap 10

\section{Introduction}

@@

  \item O'Connor's proof was written at the end of \coq V7, then rewritten at the beginning of \coq V8. Since then, \coq and its ecosystem evolved a lot (new styles, tactics, documentation tools).
          We think this evolution should benefit
          to the original proof-scripts and make their understanding easier.

        \item Finally, let us quote  Efim Zelmanov in~\cite{mathproof}
             \begin{quote}
      The purpose of a proof is \emph{understanding}.

@@

        For technical reasons --- mainly in order to make easier the installation and use of its sub-libraries, we split the project
into two main parts: Goedel~\cite{Goedel} and Hydra-battles~\cite{HydraBattles}.

@@

This part contains comments, examples  and exercises about Russel O'Connor's work on G\"{o}del's first incompleteness theorem  \cite{Godel1986-GDECW}.
O'Connor's work was published in 2005~\cite{OConnor05}, and released as a user-contribution of the \coq proof assistant.
This work is now maintained by Coq community~\cite{CoqCommunity} volunteers and split into two projects: Goedel~\cite{Goedel} and Hydra-battles~\cite{HydraBattles}.

@@

\begin{itemize}
\item \texttt{theories/goedel/}: Proofs which depend on 
\texttt{CoqPrime} package.
\item  \texttt{theories/ordinals/Ackermann/} : all the rest:
 definition of primitive recursive functions, first-order  logic,
Peano Arithmetics, G\"{o}del's encoding.
\item Some additions we made: examples, exercices, new notations, etc.,  are stored in a specific directory \texttt{theories/ordinal/MoreAck/}.
\end{itemize}

>>>>

\section{Introduction}
This part contains comments, examples  and exercises about Russel O'Connor's work on G\"{o}del's first incompleteness theorem  \cite{Godel1986-GDECW}.
O'Connor's work was published in 2005~\cite{OConnor05}, and released as a user-contribution of the \coq proof assistant.
This work is now maintained by Coq community~\cite{CoqCommunity} volunteers and split into two projects: Goedel~\cite{Goedel} and Hydra-battles~\cite{HydraBattles}.

@@

  \item O'Connor's proof was written at the end of \coq V7, then rewritten at the beginning of \coq V8. Since then, \coq and its ecosystem evolved a lot (new styles, tactics, documentation tools, etc.).
          We think this evolution should benefit
          to the original proof-scripts and make their understanding easier.

        \item Finally, let us quote  Efim Zelmanov.
             \begin{quote}
      ``The purpose of a proof is \emph{understanding}'' ~\cite{mathproof}

@@

        For technical reasons --- mainly in order to make simpler the installation and use of its sub-libraries, we split the project
into two main parts: Goedel~\cite{Goedel} and Hydra-battles~\cite{HydraBattles}.

@@

@@

\begin{itemize}
\item \texttt{theories/goedel/}: Proofs which depend on 
\texttt{CoqPrime} package.
\item  \texttt{theories/ordinals/Ackermann/} : all the rest:
 definition of primitive recursive functions, first-order  logic,
Peano Arithmetic, G\"{o}del's encoding.
\item Some additions we made: examples, exercices, new notations, etc.,  are stored in a specific directory \texttt{theories/ordinal/MoreAck/}.
\end{itemize}

\subsection{The \texttt{Ackermann} sub-directory}

The following main topics are studied in  \texttt{theories/ordinals/Ackermann/}: 
The following list presents the main modules 
in a dependance-compatible order.

\begin{description}

 \item[Primitive Recursive Functions]
  \mbox{}

 This topic is discussed in Chapter~\vref{chapter:primrec}.

  \begin{itemize}
\item
\href{../theories/html/hydras.Ackermann.extEqualNat.html}{Ackermann.extEqualNat}
  \item 
  \href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}
 \item 
  \href{../theories/html/hydras.Ackermann.cPair.html}{Ackermann.cPair}

\item 
  \href{../theories/html/hydras.MoreAck.PrimRecExamples.html}{MoreAck.PrimRecExamples}  
 \item 
  \href{../theories/html/hydras.MoreAck.Ack.html}{MoreAck.Ack}

\item
  \href{../theories/html/hydras.MoreAck.AckNotPR.html}{MoreAck.AckNotPR}

Ackermann function is not primitive recursive

\item[First Order Logic]
  \mbox{}

This part presents \coq definitions and basic properties of first-order languages and proofs.

  \begin{itemize}
  \item \href{../theories/html/hydras.Ackermann.fol.html}{Ackermann.fol}
 \item \href{../theories/html/hydras.Ackermann.folProp.html}{Ackermann.folProp}
\item \href{../theories/html/hydras.Ackermann.folProof.html}{Ackermann.folProof}
\item \href{../theories/html/hydras.Ackermann.model.html}{Ackermann.model}
\item \href{../theories/html/hydras.Ackermann.code.html}{Ackermann.code}
 \item 
  \href{../theories/html/hydras.Ackermann.prLogic.html}{Ackermann.prLogic}

\item \href{../theories/html/hydras.Ackermann.codeList.html}{Ackermann.codeList}
\item \href{../theories/html/hydras.Ackermann.codeFreeVar.html}{Ackermann.codeFreeVar}

\item \href{../theories/html/hydras.Ackermann.checkPrf.html}{Ackermann.checkPrf}
\item \href{../theories/html/hydras.Ackermann.wellFormed.html}{Ackermann.wellFormed}
\item \href{../theories/html/hydras.Ackermann.codeSubTerm.html}{Ackermann.codeSubTerm}
\item \href{../theories/html/hydras.Ackermann.codeSubFormula.html}{Ackermann.codeSubFormula}

\item[Natural Deduction]
 \mbox{}
Thanks to the \emph{Deduction Theorem}, we prove many 
lemmas about provability in first-order-logic, many of them can be considered as natural deduction rules.

\begin{itemize}
\item \href{../theories/html/hydras.Ackermann.Deduction.html}{Ackermann.Deduction}
\item \href{../theories/html/hydras.Ackermann.folLogic.html}{Ackermann.folLogic}
\item \href{../theories/html/hydras.Ackermann.folLogic2.html}{Ackermann.folLogic2}
\item \href{../theories/html/hydras.Ackermann.folLogic3.html}{Ackermann.folLogic3}
\item \href{../theories/html/hydras.Ackermann.folReplace.html}{Ackermann.folReplace}
\item \href{../theories/html/hydras.Ackermann.subProp.html}{Ackermann.subProp}
\item \href{../theories/html/hydras.Ackermann.subAll.html}{Ackermann.subAll}
 \item  \href{../theories/html/hydras.MoreAck.FolExamples.html}{MoreAck.FolExamples}
\end{itemize}

\item [Languages of Arithmetic]
\mbox{}

\begin{itemize}
\item \href{../theories/html/hydras.Ackermann.Languages.html}{Ackermann.Languages}
\item \href{../theories/html/hydras.Ackermann.LNN.html}{Ackermann.LNN}
\item \href{../theories/html/hydras.Ackermann.LNT.html}{Ackermann.LNT}
\item \href{../theories/html/hydras.Ackermann.NN.html}{Ackermann.NN} Axioms for Natural Numbers and basic properties.
\item \href{../theories/html/hydras.Ackermann.NNtheory.html}{Ackermann.NNtheory}
\item \href{../theories/html/hydras.Ackermann.PA.html}{Ackermann.PA} Peano Arithmetic: axioms  and first properties.
\item \href{../theories/html/hydras.Ackermann.LNN2LNT.html}{Ackermann.LNN2LNT}
\item \href{../theories/html/hydras.Ackermann.NN2PA.html}{Ackermann.NN2PA}

\item \href{../theories/html/hydras.Ackermann.PAtheory.html}{Ackermann.PAtheory}
\item \href{../theories/html/hydras.Ackermann.PAconsistent.html}{Ackermann.PAconsistent}

\item \href{../theories/html/hydras.Ackermann.codePA.html}{Ackermann.codePA}

\item \href{../theories/html/hydras.Ackermann.codeNatToTerm.html}{Ackermann.codeNat2Term}
\item \href{../theories/html/hydras.Ackermann.wConsistent.html}{Ackermann.wConsistent}
\item \href{../theories/html/hydras.Ackermann.expressible.html}{Ackermann.expressible}

\item \href{../theories/html/hydras.MoreAck.LNN_Examples.html}{MoreAck.LNN\_Examples}
\end{itemize}

\item[Modules dependent on \texttt{CoqPrime}]

\mbox{}

  \begin{itemize}
  \item \href{../theories/html/Goedel.PRrepresentable.html}{Goedel.PRrepresentable}
 \item \href{../theories/html/Goedel.fixPoint.html}{Goedel.fixPoint}
 \item \href{../theories/html/Goedel.codeSysPrf.html}{Goedel.codeSysPrf}
 \item \href{../theories/html/Goedel.rosser.html}{Goedel.rosser}
 \item \href{../theories/html/Goedel.goedel1.html}{Goedel.goedel1}
 \item \href{../theories/html/Goedel.rosserPA.html}{Goedel.rosserPA}
 \item \href{../theories/html/Goedel.goedel2.html}{Goedel.goedel2}
  \end{itemize}
\end{description}
